
---
title: "Web scraping week 2"
output: html_document
---

```{md, echo=F, include=F, eval=F}


<details>
  <summary>Summary Goes Here</summary>
  ...this is hidden, collapsable content...
</details>

# output:
#   md_document:
#     toc: true
#     variant: markdown_github
#   output_file: README.md
#   

  
  
```

```{r}

library(rvest)
library(data.table)

```

Typical HTML process task:

* Create a function that will process one page and return with a data frame with one line
* Create the links that you want to process, you also can write a function that will extract the links first then save them into a vector
* `lapply` your function to your links, you will get a list of data frames
* `rbindlist` your result into one dataframe 



# Coindesk
```{r}
t <- read_html('https://www.coindesk.com/tag/bitcoin/')

title <- 
t %>% 
  html_nodes('.card-title') %>% 
  html_text()

link <- 
paste0('https://www.coindesk.com',
  t %>% 
  html_nodes('.card-title') %>%
  html_attr('href')
)

teaser <- 
t %>% 
  html_nodes('.content-text') %>% 
  html_text()
  
df <- data.frame('title' = title, 'link'= link, 'teaser'= teaser)


get_coindesk_one_page <- function(url) {
  t <- read_html(url)
  
  title <- 
  t %>% 
    html_nodes('.card-title') %>% 
    html_text()
  
  link <- 
  paste0('https://www.coindesk.com',
    t %>% 
    html_nodes('.card-title') %>%
    html_attr('href')
  )
  
  teaser <- 
  t %>% 
    html_nodes('.content-text') %>% 
    html_text()
    
  df <- data.frame('title' = title, 'link'= link, 'teaser'= teaser)
  return(df)
}


links <- paste0('https://www.coindesk.com/tag/bitcoin/', 1:5, '/')

list_of_pages <- lapply(links, get_coindesk_one_page)
df <- rbindlist(list_of_pages)

```




# Infoworld scraper
```{r}

url <- 'https://www.infoworld.com/category/data-science/'

get_one_page <- function(url) {
  print(url)
  t <- read_html(url)
  
  boxes <- t %>% html_nodes('.river-well')
  
  list_of_boxes <- lapply(boxes, function(x){
    
  title <- 
    x%>% 
      html_nodes('.post-cont a')%>%
      html_text() 
    
    
  relative_link <- 
    x%>% 
      html_nodes('.post-cont a')%>%
      html_attr('href')
  
  link <- paste0('https://www.infoworld.com', relative_link)
  
  teaser <-
    x  %>%
      html_nodes('h4')%>%
      html_text()
  #
    return(data.frame('title'= title, 'teaser'= teaser, 'link'= link))
  #
  })
  one_page <- rbindlist(list_of_boxes) 
 return(one_page)
}  

df <- get_one_page(url = url)

links <- paste0('https://www.infoworld.com/napi/tile?def=loadMoreList&pageType=index&catId=3781&category=3781&includeMediaResource=true&createdTypeIds=1&categories=%5B3781%5D&days=-730&pageSize=20&offset=0&ignoreExcludedIds=true&brandContentOnly=false&includeBlogTypeIds=1%2C3&includeVideo=true&liveOnly=true&sortOrder=date&locale_id=0&startIndex=',seq(0,60, 20)  )

list_of_dfs<- lapply(links, get_one_page)

final_df <- rbindlist(list_of_dfs)

head(final_df,1)






```


# Yachtworld scraper
The base url is https://www.yachtworld.co.uk/boats-for-sale/


```{r}
# scraper for one page 
url <- 'https://www.yachtworld.co.uk/yacht/2021-ryck-280-8036770/'
t_list <- list()

t <- read_html(url)
t_list[['title']] <- t %>% html_node('.heading') %>% html_text()
t_list[['length']] <- t %>% html_nodes('.boat-length') %>% html_text()
t_list[['price']] <- t %>% html_nodes('.payment-total') %>% html_text()
t_list[['location']] <- t %>% html_node('.location') %>% html_text()


keys <- t %>% html_nodes('.datatable-title') %>% html_text()
values <- t %>% html_nodes('.datatable-value') %>% html_text()
if (length(keys)==length(values)) {
  for (i in 1:length(keys)) {
    t_list[[keys[i]]] <- values[i]
  }
}



get_one_yachts  <- function(url) {
  t_list <- list()
  
  t <- read_html(url)
  t_list[['title']] <- t %>% html_node('.heading') %>% html_text()
  t_list[['length']] <- t %>% html_nodes('.boat-length') %>% html_text()
  t_list[['price']] <- t %>% html_nodes('.payment-total') %>% html_text()
  t_list[['location']] <- t %>% html_node('.location') %>% html_text()
  
  
  keys <- t %>% html_nodes('.datatable-title') %>% html_text()
  values <- t %>% html_nodes('.datatable-value') %>% html_text()
  if (length(keys)==length(values)) {
    for (i in 1:length(keys)) {
      t_list[[keys[i]]] <- values[i]
    }
  }
  return(t_list)

}



```


```{r}
links <- c('https://www.yachtworld.co.uk/yacht/2019-jeanneau-nc-37-8469810/',
           'https://www.yachtworld.co.uk/yacht/2022-bestevaer-53-motoryacht-8218108/',
           'https://www.yachtworld.co.uk/yacht/1986-motor-yacht-38m-nicolini-8569109/')


data_list <- lapply(links, get_one_yachts)

df <- rbindlist(data_list, fill = T)


```
